### 2024-03-28 doc/sections/introduction.tex
Minor fixes

We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.

@@

The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
The phase space model defines duals by means of double negation with respect to the monoidal structure, which means that attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
\wen{%
      I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}
\bob{%
      I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely. So I think it is unlikely that phase spaces can be adapted to BV.}
\wen{%
      Gave it a shot.}

>>>>

We present an algebraic semantics and semantic proof of cut-elimination for the multiplicative-additive system MAV~\cite{Horne15:mav}, which extends the basic system BV\footnote{
      BV stands for \underline{B}asic System \underline{V}irtual, owing to an early interpretation of CCS interaction as the pairwise production and annihilation of virtual particles in physics~\cite[\Fn2]{Horne15:mav}.
}~\cite{Guglielmi99:bv,Guglielmi07:sis} with the additives of multiplicative-additive linear logic~\cite[MALL]{Girard87:ll}.
The proof is constructive and mechanised in Agda~\cite{Agda264}.

@@

The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
The phase space model derives duals by means of double negation with respect to the monoidal structure, which means that any connective has a derived dual. Attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.

### 2024-03-28 doc/sections/mav-mechanisation.tex
Minor fixes

We developed the proof in the previous two sections in the Agda proof
assistant \cite{agda}. The source code for this development is
available at this URL:
\begin{center}
  \url{https://github.com/bobatkey/semantic-cut-elimination}
\end{center}

The formalisation uses setoids to represent sets, reusing definitions
from the Agda Standard Library \cite{agda-stdlib}. Each of the
definitions and propositions above links to the corresponding part of
the development.

>>>>

We developed the proof in the previous two sections in the Agda proof
assistant \cite{Agda264}. The source code for this development is
available at this URL:
\begin{center}
  \url{https://github.com/bobatkey/semantic-cut-elimination}
\end{center}

The formalisation uses setoids to represent sets, reusing definitions
from the Agda Standard Library \cite{AgdaStdlib20}. Each of the
definitions and propositions above links to the corresponding part of
the development.

### 2024-03-28 doc/sections/mav-syntax.tex
Minor fixes

@@

A derivation is in \emph{normal form} if it does not use \cref{rule:Cut} and \cref{rule:Axiom} is restricted to \cref{rule:AtomAxiom}.
\begin{displaymath}
  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
     & \vInferFrom
     & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
     & \RuleLabel{AtomAxiom}
  \end{array}
\end{displaymath}
These restrictions correspond to the outcome of cut elimination and identity expansion, respectively.
\begin{remark}
  In BV, the structural connectives are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
  % The equations defining duality are usually included in the decidable equality on structures.
  Inferences, derivations, and proofs are presented vertically, as (\ref{notation:vlin}), (\ref{notation:vlde}), and (\ref{notation:vlpr}), respectively.
  \begin{center}
    $\inlineequation[notation:vlin]{%
        \vlderivation{\vlin{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlde]{%
        \vlderivation{\vlde{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlpr]{%
        \vlderivation{\vlpr{}{}{\vP}}}$
  \end{center}
\end{remark}

>>>>

Structure contexts are one-hole contexts over structures. Plugging ($\vC\vPlug\vP$) replaces the hole in $\vC$ with $\vP$.
  \vC,\vD
  \Coloneq \vEmpty
  \mid     \vC\vSeq \vQ
  \mid     \vP\vSeq \vD
  \mid     \vC\vTens\vQ
  \mid     \vP\vTens\vD
  \mid     \vC\vParr\vQ
  \mid     \vP\vParr\vD
  \mid     \vC\vWith\vQ
  \mid     \vP\vWith\vD
  \mid     \vC\vPlus\vQ
  \mid     \vP\vPlus\vD

@@

A derivation is in \emph{normal form} if it does not use \cref{rule:Cut} and \cref{rule:Axiom} is restricted to \cref{rule:AtomAxiom}.
\begin{displaymath}
  \begin{array}{lcl@{\hspace{0.5cm}}|@{\hspace{0.5cm}}l}
    \makebox[\vInferFromDefnWidthOfLHS][l]{$\vNeg\va\vParr\vPos\va$}
     & \vInferFrom
     & \makebox[\vInferFromDefnWidthOfRHS][l]{$\vUnit$}
     & \RuleLabel{AtomAxiom}
  \end{array}
\end{displaymath}
These restrictions correspond to the outcome of cut elimination and identity expansion, respectively.
\begin{remark}
  In BV, the structural connectives are usually presented as lists, distinguished only by their brackets: $\vP\vTens\vQ$ is written as $\vls(\vP;\vQ)$; $\vP\vParr\vQ$ is written as $\vls[\vP;\vQ]$; and $\vP\vSeq\vQ$ is written as $\vls<\vP;\vQ>$.
  % The equations defining duality are usually included in the decidable equality on structures.
  Inferences, derivations, and proofs are presented vertically, as (\ref{notation:vlin}), (\ref{notation:vlde}), and (\ref{notation:vlpr}), respectively.
  \begin{center}
    $\inlineequation[notation:vlin]{%
        \vlderivation{\vlin{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlde]{%
        \vlderivation{\vlde{}{}{\vP}{\vlhy{\vQ}}}}$
    \qquad
    $\inlineequation[notation:vlpr]{%
        \vlderivation{\vlpr{}{}{\vP}}}$
  \end{center}
  The relation between the deductive system for BV and rewrite systems is well-known, \eg by Kahramanogullari~\cite{Kahramanogullari08:maude}, who implements proof search for several deep inference systems in Maude~\cite{ClavelDELMMQ02:maude}.
\end{remark}
